A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-13 docs/icccn2009/paper.tex
Added section on DSP Implementation
git-svn-id: svn://localhost/netbeams/trunk@383 559edde2-a4d4-44e0-96fc-4035e40d7396

\subsection{DSP Broker}

@@

@@

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}.
Since Sun Microsystems does not support its JDK for the Gumstix, we
use JamVM \cite{jamvm01} as the Java virtual machine implementation
and GNU Classpath \cite{classpath01} for the runtime libraries. We
have implemented various DSP Components that implement the
functionality needed for NetBEAMS. On the far left of Figure
\ref{FIG_NETBEAMS} is the actual sensor; in our case the
aforementioned YSI Sonde. The YSI Sonde DP \ding{192} uses the RS232 standard
to read the physical measurements from the device over a serial port.
This component converts the physical measurements into a DSP-specific
message. Figure \ref{FIG_DSP_YSI_DATA} depicts the YSI Sonde's
specific message format which includes each measurement data point,
described in Table \ref{TAB_SONDE_MEASUREMENTS}.

@@

The SondeDataContainerType defines the payload of messages generated
by the YSI Sonde DP. As all DSP messages, it is derived from the
AbstractMessageContent. The payload mainly consists of the
SondeDataType that defines all the sensor data that the YSI Sonde is
capable of producing. The YSI Sonde DP uses the RS232 to query the
physical device for its data in regular intervals. The measurements
are then converted into a DSP message and forwarded to the DSP Broker
from there they are forwarded to the remote communication component
described in the next section.  The YSI Sonde DP can also be
configured via special DSP messages, to direct the Sonde to change its
sampling frequency.  These property messages originate from a web
management interface (component \ding{197} in Figure \ref{FIG_NETBEAMS}).

>>>>

\subsection{DSP Broker}
\label{SEC_DSP_BROKER}

@@

\subsection{DSP Implementation}

The DSP is implemented in Java using the OSGi platform. OSGi
\cite{osgi} is a Java-based component system. So-called bundles, which
are self-contained Java JAR files, can be deployed and undeployed at
runtime via special purpose class loaders. In fact, the API of the DSP
is inspired by OSGi. All DSP Components depicted in Figure
\ref{FIG_NETBEAMS} are implemented as OSGi bundles. The DSP Broker
discussed in Section \ref{DSP_BROKER} is mapped to an OSGi bundle as well.

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}.
Since Sun Microsystems does not support its JDK for the Gumstix, we
use JamVM \cite{jamvm01} as the Java virtual machine implementation
and GNU Classpath \cite{classpath01} for the runtime libraries. In the
following sections we provide further details of some of the DSP
Components that we have implemented as part of the NetBEAMS project.

@@

On the far left of Figure \ref{FIG_NETBEAMS} is the actual sensor; in
our case the aforementioned YSI Sonde. The YSI Sonde DP \ding{192}
uses the RS232 standard to read the physical measurements from the
device over a serial port.  This component converts the physical
measurements into a DSP-specific message. Figure
\ref{FIG_DSP_YSI_DATA} depicts the YSI Sonde's specific message format
which includes each measurement data point, described in Table
\ref{TAB_SONDE_MEASUREMENTS}.

@@

The \texttt{SondeDataContainerType} defines the payload of messages generated
by the YSI Sonde DP. As all DSP messages, it is derived from the
\texttt{AbstractMessageContent}. The payload mainly consists of the
\texttt{SondeDataType} that defines all the sensor data that the YSI Sonde is
capable of producing. The YSI Sonde DP uses the RS232 to query the
physical device for its data in regular intervals. The measurements
are then converted into a DSP message and forwarded to the DSP Broker
from there they are forwarded to the remote communication component
described in the next section.  The YSI Sonde DP can also be
configured via special DSP messages, to direct the Sonde to change its
sampling frequency.  These property messages originate from a web
management interface (component \ding{197} in Figure \ref{FIG_NETBEAMS}).
